Training a Gaming Agent on Brainwaves

### 2020-08-22 review/response.letter.tex

However, I am not sure if there is something new in the paper compared to the 2010 proof-of-concept (Iturrate et al.: Robot Reinforcement Learning using EEG-based reward signals). The presentation style seems a bit confusing and needs serious improvements. Background is very limited (some are incorporated in the introduction) and substantial work is required. There has been a lot of work in BCIs over the past decade and some in the area of games.

\begin{quotation}
{\color{blue}
We conducted a new BCI and games literature review and updated the Introduction accordingly, adding more updated background.  We highlight now what we think is our contribution, which is a simple game that can be used to trigger the ErrP response in a simple scenario that can be used to train an agent.  We were unable to find a similar work from that same perspective.  
}
\end{quotation}

From the scientific part, the results are not so convincing. In particular, the proposed idea does not seem to be too practical method. The classification does not provide something significant as it stands at the moment. The sample used is also quite small and the complexity of the game is limited.

\begin{quotation}
{\color{blue}
Issues raised by the Reviewer are accurate and timely described.  We aimed to find a suitable game that at the same time can be trained with a Reinforcement Learning technique and that triggered the ErrP response as well.  We modified the manuscript, emphasized three results of our experiments.  First we show that the basic Q-Learning algorithm is robust to noisy signals.  Additionally,  we show the futility of transfer learning approaches using the brainwave signals, and finally that the cumulative contribution of the rewards obtained from different subjects enhances the performance of an agent.
}
\end{quotation}

@@

Nevertheless, the paper could be improved in many ways. An obvious point would be to improve the classifiers. Apart from this, I would suggest that authors would look at ways of manipulating the stimulus, stimulus presentation or giving out incentives to participants.

\begin{quotation}
{\color{blue}
We added a new classifier and performed two more experiments.  First we included kNeighbours as a new classification algorithm.  This can be seen in Section C and in Figure 3.  In that same Figure, we also added results obtained while performing signal averaging to enhance the SNR of the ErrP component. Moreover, we performed a complete transfer learning experiment, verifying if it was possible to improve the efficiency of the gaming agent and verified that the best results for the improvement (i.e. reduction) on the average number of steps, required to reach the target in 200 plays, is achieved when a classifier is trained with ErrP signals from the same subject that is used to identify the ErrP.    This is added in Section IV and in Figure 7.
On the other hand, the structure of the game scenario allows to easily extend the experiments to verify what is the outcome of manipulating the stimulus, their presentation or the influence on the results if incentives are given to participants.  We added this compelling ideas to the Section IV.
}
\end{quotation}

@@

39 This information is used to make a gaming agent improves its operational performance using electroencephalography (EEG) signals as feedback of the performed task, obtained from an observational human critic.
//There is a grammar issue. I don’t understand this sentence.

\vspace{2em}
\begin{quotation}
{\color{blue}
We modified the sentence.  We thanks the reviewer for pointing out this issue.
}
\end{quotation}
\vspace{2em}

54 RL should be defined in main body of the paper. Also the term ‘agent’ needs to be defined/clarified. How does it relate to the Game Manager from Figure 1?

\vspace{2em}
\begin{quotation}
{\color{blue}
The acronym was revised and we also verified all the other acronyms used in the text.  The term "agent" was defined and presented in the Introduction, and their relation with the Game Manager in Figure 1 was established.
}
\end{quotation}
\vspace{2em}

@@

17 col 2 Recently, this technique has seen a come-back. // this is not scientific language

\vspace{2em}
\begin{quotation}
{\color{blue}
This mistake has been corrected.  We apologize for the bad choice of words.
}
\end{quotation}
\vspace{2em}

58 col 3 The precision of 25.125 is inappropriate P2, 46 col 2 What is “state information”?

\vspace{2em}
\begin{quotation}
{\color{blue}
The precision was adjusted to two decimals for the age mean and the standard deviation.  We removed  "state information" and replaced the wording of the phrase in order to clarify more clearly the information that we wanted to convey:  we refer to state information to the sequence of movements that the gaming agent performs on the game.
}
\end{quotation}
\vspace{2em}

@@

P3, 2 red normally indicates an error

\vspace{2em}
\begin{quotation}
{\color{blue}
We understand the Reviewer's point, and we agree with her/him that red is not the right color to represent the completion of a task in the game, and in this case it may have cognitive implications regarding the generalized concept that red indicates an error.   It is known that the ErrP response may be affected by colors and shapes (Eimer 1997, \textit{An event-related potential (ERP) study of transient and sustained visual attention to color and form}).  The experiments that we performed were implemented with the board showed on Figure 2 of the manuscript.  We added this very important issue at the conclusions in relation with possible future works.
}
\end{quotation}
\vspace{2em}

P3, 11 I assume that the “observational human critic” is the player/participant/subject/human observer. This role should be clarified and terminology used consistently.

\vspace{2em}
\begin{quotation}
{\color{blue}
Absolutely.  We preferred to use OHC "observational human critic" to emphasize what the subject is actually doing while using the system.  We clarified this notation at the Introduction and along the manuscript.
}
\end{quotation}
\vspace{2em}

@@

\vspace{2em}
\begin{quotation}
{\color{blue}
Excellent.  We added that information.
}
\end{quotation}
\vspace{2em}

P4, 32 Hence, following the iterative procedure based on Equation 1, the Q-Table is updated in each iteration. After the algorithm finishes iterating throughout all the training episodes, the Q-Table is stored to test the performance of the agent.
// Will the game always terminate? How long does the game take? Does smooth progression toward finish affect the err potential?

\vspace{2em}
\begin{quotation}
{\color{blue}

When the gaming agent moves randomly on the board of Figure 2, it takes on average 100 steps to arrive to the final location on the grid.  Each step, the movement direction is performed once every 2 seconds, so on average it takes around 200 seconds to finish the game.  After training during \textit{run sessions} (check new Section II.F), the agent starts to use the Q-Table to decide the next movement.  However, the Q-Table could potentially end up producing endless loops or deadlocks so if the steps count arrives to 200 the game is interrupted and it starts all over again.
So far we didn't test if the Error Potential is affected by the smooth progression toward the end, which is indeed something interesting to verify in this simple scenario.  We added this very interesting extension in Section IV.

@@

P4 referring to Fig 6; a comparison ROC curve with subject 1 would be more interesting

\vspace{2em}
\begin{quotation}
{\color{blue}
We added on Figure 5(now) all the ROC curves that we obtained for all the different subjects, including the one for Subject 1.  
}
\end{quotation}
\vspace{2em}

P5, 34 what is meant by “experiences”?

\vspace{2em}
\begin{quotation}
{\color{blue}
We added a new Section II.F to clarify this part of the experiment which was not explained at all.  First we rewrote how we separated the two parts of the experiment, the "Cognitive Game Procedure" and the "Gaming Agent Learning Procedure".   We replaced "experiences" with \textit{run session}.  This all is explained in the above-mentioned section.
}
\end{quotation}
\vspace{2em}

@@

P5, 29 col 2 – remove Average steps per Q-Table legend.

\vspace{2em}
\begin{quotation}
{\color{blue}
This was modified in all the Figures, adjusting fonts and labels.  We appreciate a lot the time to point out this issue.
}
\end{quotation}
\vspace{2em}

P5 50, col 2 The collected data show that ErrP signals can in fact be classified and used to train an agent effectively.
// how has effectiveness been determined here?

\vspace{2em}
\begin{quotation}
{\color{blue}
Each time the gaming agent plays this simple game, it takes on average around 100 steps to reach the target spot.   We asked an observational human critic to watch the gaming agent play the game, while we recorded their brainwaves.  We trained first a classifier to be able to recognize Error Potentials from these brainwaves.  We started the game again, and the gaming agent started to move around the board, but this time once an Error Potential was identified from the brainwaves, it was used as a negative reward to train a new Q-Table for the agent.  The game was iteratively repeated, but the gaming agent used the Q-Table that was updated in the previous run session.
We verified that by doing this experiment, the agent required less and less steps on average to reach the goal until it arrives to the optimal number of around 10 steps.  We found that although the effectiveness of this improvement depended on the accuracy of the classifier, even with very low values (just above chance level), the agent learns and the number of average number of steps is reduced.
We verified that if trained the agent with sham signals, completely uncorrelated with the reward, the agent learned nothing, and the average number of steps was not reduced at all.
Finally, we also verified that if we train a classifier with Error Potentials from one subject and used that classifier to provide the rewards for the experiment, the number of steps is not reduced, and that do not depend on the subjects, is an intrinsic result which is produced when intermixing the OHCs.  Only the usage of a trained classifier from the same OHC produces this improvement.
Finally, we verified that rewards obtained from different OHCs, can be used to improve the performance of the gaming agent collaboratively.
}
\end{quotation}
\vspace{2em}

@@

\vspace{2em}
\begin{quotation}
{\color{blue}
Yes, the Reviewer is correct.  We modified this sentence to state more clearly the message that we wanted to convey, which is, that results are completely subject dependent.  But that even when many action should be tagged as "wrong" (triggering an ErrP) only with a few of them right, it is enough to train the agent towards the optimal solution.
}
\end{quotation}
\vspace{2em}

P6, 56
Results show that training a classifier with data of one subject, but using it
to classify the events of experiences of another subject does
not lead to an improvement on the performance of the agent.

// could a pre-trained generic classifier provide a better initial state, subsequently trained with observer data to converge more quickly?
Are there differential err potential for up, down, left, right?

\vspace{2em}
\begin{quotation}
{\color{blue}
The statement is absolutely right.  We extended this experience per Reviewer's suggestion and we verified that effectively the only combination of training/testing in the recognition of ErrP that produces an improvement on the performance of the agent is the one that uses information from the same subject (check new Figure 7).   We think a generic-classifier to identify ErrP potentials for any subject (i.e. without calibration) is a research goal of the BCI community because this will allow to have more robust, easier to use, with shorter setups  BCI devices (Suller 2012,\textit{Online use of error-related potentials in healthy users and people with severe motor impairment increases performance of a P300-BCI}).  If such a generic pre-trained classifier could be conceived, this simple game can be used to verify if the number of training sessions required is reduced and this will confirm that the pre-trained classifier is helping to do it more quickly.  We didn't verify if the error potential for up, down, left, right per se produces a different error potential, though we verified that in general getting farther from the target (in Manhattan distance) produces a signal which is slightly different from the one that is produced when the gaming agent moves closer to the target.  We added these very interesting lines of further exploration in Section IV.
}
\end{quotation}
\vspace{2em}

@@

Since different subjects attained different performance, all combinations of subjects used for training and testing should be inspected for the 1:1 evaluation setup.

\begin{quotation}
{\color{blue}
This is an excellent idea that we now explored with a new experiment.  We showed the results on Figure 7, where a classifier is trained to recognize ErrP signals using the information obtained from one Trainer subject and used to generate rewards for a gaming agent on a different Tester subject.  We added information about this on Section IV.
}
\end{quotation}

Maybe classification accuracy could be reported at different steps (depending on the amount of training data – gradual increasing the number of subjects)

\begin{quotation}
{\color{blue}
The classification accuracy obtained for all subject is now being shown on Figure 5 with ROC curves.  What is shown progressively is the experiment itself, where after each gaming agent training match, a new Q-Table is generated based on the rewards tagged from the brainwave session.  The agent improves their efficiency by reaching the target in a progressively less number of steps on average for each run session.
}
\end{quotation}

@@

What is the ratio of hit/no hit segments of action (epochs)?

\begin{quotation}
{\color{blue}
The ratio hit/no-hit segments is 50/50, so for each brainwave session match, as the average number of steps is around 100, it will be 50 segments of hit (moving further from the target) and 50 of no-hit (moving closer).  
}
\end{quotation}

@@

Page 3, column 2, lines 4-9. It is unclear at this stage what action from the starting point would generate an ErrP.
moves-> move

\begin{quotation}
{\color{blue}
The Reviewer is absolutely right in that there isn't any possible action that the gaming agent can perform at the beginning of the experience (the game agent is located at the upper-left corner) that may trigger an ErrP response.  We modified the phrase to emphasize the message that we wanted to convey.  Additionally, there is a very important caveat of the experiment. The gaming agent always has a 5\% chance of wandering and selecting an action randomly, regardless of their Q-Train.  This is precisely to avoid loops or deadlocks situations.

On the other hand, we fixed the pointed out grammatical error as well.
}
\end{quotation}

@@

Page 3, column 2, lines 11-13. Has the MinMax Scaler been applied in any other BCI related study or elsewhere? I think including a reference would be useful.

\begin{quotation}
{\color{blue}
We added a reference where the MinMaxScaler is used in a BCI application (new page 3, second column).
}
\end{quotation}

Page 4. Figure 3. I would suggest adding another set of bars for the grand average classification scores.

\begin{quotation}
{\color{blue}
We added a new bar on the Figure 3 where we included the obtained classification accuracy when 5 segments are ensemble averaged to produce an averaged signal (with an improved SNR in terms of the ErrP).   These scores are reported in the Figure 4 as "GrandAvg".  There is a balance to be considered because adding more segments to the averaged signal reduces the number of available samples used for training the classifier.
}
\end{quotation}

@@

Page 4, Figure 4. This figure is redundant and could be removed.

\begin{quotation}
{\color{blue}
The figure was removed, thank you very much for your comment.
}
\end{quotation}

@@

Page 5, Figure 5. The titles of the subplots would be more descriptive when replacing the letters with the corresponding subjects number.

\begin{quotation}
{\color{blue}
We agree with Reviewer's comment.  We removed the letters and replace them with subject's numbers in Figures 4 and 5.
}
\end{quotation}

@@

Page 5, column1, line 55, accumulative->cumulative

\begin{quotation}
{\color{blue}
Fixed.
}
\end{quotation}

Page 6, Figure 8. It is unclear to me what is the benefit of showing both A and B. Since the behavior is similar in both cases.

\begin{quotation}
{\color{blue}
We included now all the ROC curves for all the subjects.
}
\end{quotation}

### 2020-08-22 ErrP.tex
Subo la versión lista para subir.

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\begin{abstract}
In this study, we propose a simple game scenario that can be used to trigger a feedback response embedded in the Electroencephalographic (EEG) signals of an observation human critic that observes an agent playing a game.  Based on the model of Reinforcement Learning (RL), the gaming agent receives rewards for their actions on the game and learns its optimal policy.  These rewards are obtained by implementing a Brain-Computer Interface (BCI) system that identifies signal components called Error-related Potentials (ErrP).  These are brain signals found on EEG that can be elicited by a person who attends a recognizable error. When subjects observe the agent making a mistake this potential can be discerned by analyzing the signals which are directly related with the cognitive interpretation of an erroneous outcome or decision.  We perform an iteratively incremental experiment where the agent plays, receives rewards from an observational human critic, and updates its policy for the next match.  Our results are expressed in threefold: (i) the structure of a simple grid-based game that can elicit the ErrP signal component; (ii) low classification accuracy just above chance level that produces noisy rewards is enough to allow an agent to learn the optimal policy and solve the game; (iii) collaborative rewards from multiple observational human critics can compensate the lack of accuracy obtained from specific subjects or the difficulty of transfer learning solutions.
\end{abstract}

@@

% You must have at least 2 lines in the paragraph with the drop letter
% (should never be an issue)
\IEEEPARstart{T}{he} effectiveness of today's human–machine interaction and artificial intelligence is limited by a communication bottleneck as humans are required to translate high-level concepts into a machine-mandated sequence of instructions~\cite{Xu2020,CURSOR-CONTROL-PAPER}.   Hence, new interaction methods are required to increase the communication bandwidth between computers and human, or to produce alternative communications systems to increase the efficiency of this channel.  In this respect, video games has been widely used as test tools to assess new means of interactions~\cite{Carter2014,Barr2007}. Video gaming agents are computer programs that can sense the computer game environment, process information, and interact with it.  They are used in the context of testing and evaluating artificial intelligence algorithms that aim to win the game or to behave like a real user player~\cite{Zhao2020}.
In this work, the feedback obtained from an observational human critic (OHC) in the form of electroencephalographic (EEG) signals is used to evaluate the operational performance of a gaming agent.  Observational human critics are silent subjects observing a computer gaming agent playing the game.

@@

In order to train the agent, Reinforcement Learning (RL)~\cite{Sutton2018} comes as a natural solution for this scenario from the field of Artificial Intelligence.  This is an algorithmic learning strategy inspired on how biological agents learn by exploring their environment, and getting negative or positive feedback rewards.  This strategy aims to maximize the amount of positive rewards while keeping the number of negative feedback low.  Thus, the learning problem is  posed as a stochastic optimization strategy~\cite{Santos1999}.  Recently, this technique has been used extensively in the context of  advances in artificial intelligence~\cite{Nguyen2020}. Nonneglected is the influence of DeepBrain's AlphaGo project, which was the first to reach a very high proficiency when it won the complex game Go against several world champions~\cite{ALPHA-GO}.

@@

Previous research has explored the usage of RL with reward signals based on brain activity, recorded by an EEG-based BCI system during task execution. The papers \cite{ROBOT-CONTROL-PAPER,Kim2017,Omedes2013} have successfully demonstrated that a robot can be controlled by obtaining a reward signal from a person's brain activity which is observing the robot solve a task.  In the context of Brain Computer Interfaces a growing number of studies have demonstrated the feasibility of using ErrPs as rewards for RL schemes such as to enhance robotic behaviour~\cite{Luo2019}, to assess air traffic controllers decissions~\cite{Goh2019} or  to categorise actions as errors~\cite{Wirth2020}. Other approaches have used the signal as an important feedback for human-robot interaction or to implement shared-control strategies~\cite{Schiatti2018}.  Additionally, ErrPs have also been used in the context of games as an additional feedback channel that can be explored to improve gaming experience~\cite{Plass-OudeBos2010,kober2018bci}.

Therefore, in this work, we aim to use the information extracted from brainwaves to enhance the performance of a gaming agent.   The three contributions  are (1) a very simple game that can elicit the ErrP potential, (2) results that confirm that even when ErrP classification accuracy is low and produces a noisy reward signal, that provides enough information for an agent to learn the optimal policy and solve the simple game and (3) that collaborative rewards from multiple observational human observers can compensate the lack of accuracy obtained from specific subjects.

@@

In Section \ref{section:materials} the general layout of the cognitive game is described. Section \ref{section:calibration} outlines the processing pipeline used to detect ErrP components. The following Section \ref{learning} describes the agent learning phase.   Results and Conclusions are exposed in Sections \ref{results} and \ref{conclusions}.

@@

This first part consists in collecting signals from a person's brainwaves while they are watching a game where the agent knows the game rules but not how to win it. Hence, the agent can learn the winning strategy using the person's feedback to improve its own performance. This section describes the process of obtaining the person's brain signals that are used to make the agent more efficient.

\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{Images/complete_flow.png}
    \caption{Overview of the experimental procedure. Brainwaves are obtained by the OpenVibe Acquisition Server.  The Game Manager is responsible for generating the game screen, the game mechanics, and the game movements performed by the gaming agent.  It is also connected to the Acquisition Server to send stimulus information.  The captured information is stored by the OpenVibe Designer.  Offline, EEG signals are classified and they are linked to each game movement calculated by the Game Manager to determine proper rewards for each action.  This information is used by a Reinforcement Learning algorithm to learn a Q-Table to improve the performance of the agent that plays the game.}
    \label{diag:complete_flow}
\end{figure*}

The experimental procedure is summarized in Figure \ref{diag:complete_flow}. The central part is the retrieval of the OHC's brain activity.  This process is called brainwave session. Subjects are recruited voluntarily. They are given a consent form with questions regarding their health (previous health issues and particular visual sensitivity), habits (sleeping hours, caffeine and alcohol consumption), as well as an approval petition to collect the required data. The brainwave sessions are performed with 8 subjects, 5 males and 3 females, average age 25.12 years, standard deviation 1.54 years, range of 22-28 years. All subjects have normal vision, are right-handed and have no history of neurological disorders.

@@

The Acquisition Server has the responsibility of receiving and synchronizing the signal data from the headset and any event information from the game, and transfers it to the OpenVibe Designer application. When the subject is ready, the Game Manager and the OpenVibe Designer programs are launched and configured to communicate with the previously mentioned Acquisition Server. A brainwave session consists of several matches, each one being a game run.  At the end, all the sequence of game movements and the signal data generated for each match are saved for offline processing.

@@

\section{Signal Processing, Segmentation and Classification}
\label{section:calibration}

@@

\section{Reinforcement Learning}
\label{learning}

Each match consists of a list of game movement configurations and the associated epochs obtained from OHC's brainwaves.  The set of matches of each OHC is split into training and testing.  Training matches are used to train the classifier to identify the ErrP signal.  After a classifier is trained, the epochs extracted from the test matches are classified as hit or no-hit.  A reward for each movement in the game run is produced, based on the prediction from the classifier that correspond to that movement.  The reward can either be -1 when the event is classified as a hit or 0 when it is classified as a no-hit. The accuracy of this rewards depends on the performance of the classifier. The list of game movements and their associated reward information are used to train the agent by a variant of Reinforcement Learning called Q-Learning algorithm.

@@

\subsection{Agent Learning}
\label{q_learning_step_alg}

The Q-Table is initialized with zeros, so the initial policy for the agent is randomized.   In order for the agent to learn from the feedback generated by the OHC,  the policy which determines which action to take in a particular state is given by the agent's actions taken from the previous brainwave session match. This allows to learn the Q-Table based on the OHC's feedback from the movements the agent took, which are initially chosen pseudo-randomly, while executing the brainwave session. The previously mentioned feedback is not explicit as it comes from the interpreted brain signal data. This implies that the reward is determined by the OHC's brain activity.

Hence, following the iterative procedure based on Equation~\ref{equ:update_q_table}, the Q-Table is updated in each iteration.  After the algorithm finishes iterating through all the training episodes, the Q-Table is stored and used by the agent in the next match.

@@

Figure~\ref{fig:classifiers} show the binary classification accuracy obtained for the eight OHCs for the four different classification algorithms using a 10-fold cross validation procedure.  The best overall performance is obtained using Logistic Regression.  In addition, the classification accuracy obtained averaging 5 epochs is shown as well.   Although the signal averaging procedures improves the Signal-To-Noise-Radio (SNR) of the ErrP response, it reduces the number of data samples and produces a clear improvement only for the subjects that contain more samples (5, 3 and 7).

\begin{figure}[ht]
    \centering
    \includegraphics[scale=0.12]{revisedimages/cross_val.eps}
    \caption{Binary single trial classification score using four different classifiers while recognizing ErrP potentials for the eight OHCs.  The classification score using an ensemble average of 5 epochs is shown as well (GrandAvg). Chance Level is 0.5.}
    \label{fig:classifiers}
\end{figure}

On the other hand, Figure \ref{fig:avg_steps} shows for each OHC the average amount of steps the agent takes to reach the goal as the Q-Table is progressively trained using the reward information obtained from the prediction performed by the trained classifier. Each point corresponds to the average number of steps, in 200 repetitions, that it takes for the agent to reach the goal for a specific Q-Table. The first point represents the amount of steps the agent takes to reach the goal for a Q-Table that hasn't been trained at all, where movements are decided randomly. The next point corresponds to the amount of steps it takes to reach the goal using a policy derived from a Q-Table trained with one game match, and so on.

\begin{figure}[h!]
\begin{subfigure}{0.5\textwidth}
\centering
\includegraphics[scale=0.27]{Images/Average_steps/a.png}
\includegraphics[scale=0.27]{Images/Average_steps/b.png}
\centering
\includegraphics[scale=0.27]{Images/Average_steps/c.png}
 \includegraphics[scale=0.27]{Images/Average_steps/d.png} 
 \centering
  \includegraphics[scale=0.27]{Images/Average_steps/e.png} 
  \includegraphics[scale=0.27]{Images/Average_steps/f.png} 
  \centering
  \includegraphics[scale=0.27]{Images/Average_steps/g.png} 
  \includegraphics[scale=0.27]{Images/Average_steps/h.png} 
\end{subfigure}
\caption{Average number of steps for the agent to reach the goal when trained with rewards generated from brainwaves from OHCs 1-8. Y axis show the averaged number of steps, while x axis show the number of game matches used to cumulative train the Q-Table.}
\label{fig:avg_steps}
\end{figure}

@@

\begin{figure}[h!]
\centering
\includegraphics[scale=0.4]{Images/Average_steps/noise.eps}
\caption{Average steps using Q-Table trained with a noisy signal.}
\label{fig:avg_steps_noise}
\end{figure}

>>>>

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\begin{abstract}
In this study, we propose a simple game scenario that can be used to trigger a feedback response embedded in Electroencephalographic (EEG) signals of an observation human critic that observes an agent playing a game.  Based on a Reinforcement Learning (RL) model, the gaming agent receives rewards for their actions on the game and learns its optimal policy.  These rewards are obtained by implementing a Brain-Computer Interface (BCI) system that identifies signal components called Error-related Potentials (ErrP).  These are brain signals found on EEG that can be elicited by a person who attends a recognizable error.  We perform an experiment where rewards are obtained from observational human critics watching an agent playing randomly a game. This information is used to iteratively train the agent which receives these rewards and updates its policy improving its overall performance.  Our results are expressed in threefold: (i) the structure of a simple grid-based game that can elicit the ErrP signal component; (ii) the verification that  low classification accuracy of just above chance level that produces noisy rewards is enough to allow an agent to learn the optimal policy; (iii) collaborative rewards from multiple observational human critics can compensate the lack of accuracy or the limited scope of transfer learning schemes.
\end{abstract}

%When subjects observe the agent making a mistake this potential can be discerned by analyzing the signals which are directly related with the cognitive interpretation of an erroneous outcome or decision.

@@

% You must have at least 2 lines in the paragraph with the drop letter
% (should never be an issue)
\IEEEPARstart{T}{he} effectiveness of today's human–machine interaction and artificial intelligence is limited by a communication bottleneck as humans are required to translate high-level concepts into a machine-mandated sequence of instructions~\cite{Xu2020,CURSOR-CONTROL-PAPER}.   Hence, new interaction methods are required to increase the communication bandwidth between computers and humans, or to produce alternative communications systems to increase the efficiency of this channel.  In this respect, video games has been widely used as test tools to assess new means of interactions~\cite{Carter2014,Barr2007}. Video gaming agents are computer programs that can sense the computer game environment, process information, and interact with it.  They are used in the context of testing and evaluating artificial intelligence algorithms that aim to win the game or to behave like a real user player~\cite{Zhao2020}.
In this work, the feedback obtained from an observational human critic (OHC) in the form of electroencephalographic (EEG) signals is used to evaluate the operational performance of a gaming agent.  Observational human critics are silent subjects observing a computer gaming agent playing the game.

@@

In order to train the agent, Reinforcement Learning (RL)~\cite{Sutton2018} stands as a natural solution for this scenario from the field of Artificial Intelligence.  This is an algorithmic learning strategy inspired on how biological agents learn by exploring their environment, and getting negative or positive feedback rewards.  This strategy aims to maximize the amount of positive rewards while keeping the number of negative feedback low.  Thus, the learning problem is  posed as a stochastic optimization strategy~\cite{Santos1999}.  Recently, this technique has been used extensively in the context of  advances in artificial intelligence~\cite{Nguyen2020}. Nonneglected is the influence of DeepBrain's AlphaGo project, which was the first to reach a very high proficiency when it won the complex game Go against several world champions~\cite{ALPHA-GO}.

@@

Previous research has explored the usage of RL with reward signals based on brain activity, recorded by an EEG-based BCI system during task execution. The papers \cite{ROBOT-CONTROL-PAPER,Kim2017,Omedes2013} have successfully demonstrated that a robot can be controlled by obtaining a reward signal from a person's brain activity which is observing the robot solve a task.  Moreover, a growing number of studies have demonstrated the feasibility of using ErrPs as rewards for RL schemes such as to enhance robotic behaviour~\cite{Luo2019}, to assess air traffic controllers decissions~\cite{Goh2019} or  to categorise actions as errors~\cite{Wirth2020}. Other approaches have used the signal as an important feedback for human-robot interaction or to implement shared-control strategies~\cite{Schiatti2018}.  Additionally, ErrPs have also been used in the context of games as an additional feedback channel that can be explored to improve gaming experience~\cite{Plass-OudeBos2010,kober2018bci}.

Therefore, in this work, we aim to use the information extracted from brainwaves to enhance the performance of a gaming agent.   The three contributions  are (1) a simple game that can elicit the ErrP potential, (2) results that confirm that even when ErrP classification accuracy is low and produces a noisy reward signal, this provides enough information for an agent to learn the optimal policy and solve the simple game and (3) collaborative rewards from multiple observational human observers can compensate the lack of classification accuracy or the inefficacy of transfer learning procedures for brainwaves signals.

@@

In Section \ref{section:materials} the general layout of the cognitive game is described. Sections \ref{brainwavesession} and \ref{cognitive_experiment_details} outlines the cognitive game procedure used to obtain rewards in the form of ErrP components. Section \ref{q_learning_step_alg} describes the gaming agent learning procedure.   Lastly, results and conclusions are exposed in Sections \ref{results} and \ref{conclusions}.

@@

The experimental procedure is summarized in Figure \ref{diag:complete_flow}. The proposed system has two distinct parts. This first part consists in collecting signals from a person's brainwaves while they are watching an agent playing a game.  The agent knows the game rules but not how to win it. The second part, the gaming agent learning phase, is where the agent can learn the winning strategy using the person's feedback to improve its own performance.

\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{Images/complete_flow.png}
    \caption{Overview of the experimental procedure. Brainwaves are obtained by the OpenVibe Acquisition Server.  The Game Manager is responsible for generating the game screen, the game mechanics, and the game movements performed by the gaming agent.  It is also connected to the Acquisition Server to send stimulus information.  The captured information is stored by the OpenVibe Designer.  Offline, EEG signals are classified and they are linked to each game movement calculated by the Game Manager to determine proper rewards for each action.  This information is used by a Reinforcement Learning algorithm to learn iteratively a Q-Table to improve the performance of the agent that plays the game.}
    \label{diag:complete_flow}
\end{figure*}

\subsection{Brainwave Session}
\label{brainwavesession}

The central part is the retrieval of the OHC's brain activity.  This process is called brainwave session. Subjects are recruited voluntarily. They are given a consent form with questions regarding their health (previous health issues and particular visual sensitivity), habits (sleeping hours, caffeine and alcohol consumption), as well as an approval petition to collect the required data. The brainwave sessions are performed with 8 subjects, 5 males and 3 females, average age 25.12 years, standard deviation 1.54 years, range of 22-28 years. All subjects have normal vision, are right-handed and have no history of neurological disorders.

@@

The Acquisition Server has the responsibility of receiving and synchronizing the signal data from the headset and any event information from the game, and transfers it to the OpenVibe Designer application. When the subject is ready, the Game Manager and the OpenVibe Designer programs are launched and configured to communicate with the previously mentioned Acquisition Server. A brainwave session consists of several matches, each one being a game play.  At the end, all the sequence of game movements and the signal data generated for each match are saved for offline processing.

@@

\subsection{Signal Processing, Segmentation and Classification}
\label{section:calibration}

@@

\subsection{Reinforcement Learning}
\label{learning}

Each match consists of a list of game movement configurations and the associated epochs obtained from OHC's brainwaves.  The set of matches of each OHC is split into training and testing.  Training matches are used to train the classifier to identify the ErrP signal.  After a classifier is trained, the epochs extracted from the test matches are classified as hit or no-hit.  A reward for each movement in the match is generated based on the prediction from the classifier that correspond to that movement.  The reward can either be -1 when the event is classified as a hit or 0 when it is classified as a no-hit. The accuracy of this rewards depends on the performance of the classifier. The list of game movements and their associated reward information are used to train the agent by a variant of Reinforcement Learning called Q-Learning algorithm.

@@

\subsection{Gaming Agent Learning Procedure}
\label{q_learning_step_alg}

This procedure uses the testing matches from brainwave sessions produced during the cognitive game procedure phase, and their components are schematized in Figure~\ref{diag:complete_flow}.

This phase is divided in a sequence of a run session, and a gaming agent training match.  During the run session, the agent plays 200 matches guided by a specific Q-Table with a remaining 5\% chance of a randomly selected movement left out to reduce deadlocks and loops.  Following the run session, the agent performs a single gaming agent training match.  The gaming agent starts with a Q-Table initialized with zeros, so the initial policy for the agent is randomized.   In order for the agent to learn from the feedback generated by the OHC,  the policy which determines which action to take in a particular state is given by the agent's actions taken from one brainwave session match. This allows to learn the Q-Table based on the OHC's feedback from the movements the agent took, which are chosen pseudo-randomly while executing the brainwave session. The previously mentioned feedback is not explicit as it comes from the interpreted brain signal data. This implies that the reward is determined by the OHC's brain activity.

Hence, following the iterative procedure based on Equation~\ref{equ:update_q_table}, the Q-Table is updated in each gaming agent training match. After the algorithm finishes replicating all the steps from the brainwave session match, the Q-Table is stored and used by the agent in the next run session.

@@

Figure~\ref{fig:classifiers} show the binary classification accuracy obtained for the eight OHCs for the five different classification algorithms using a 10-fold cross validation procedure.  The best overall performance is obtained using Logistic Regression.  In addition, the classification accuracy obtained averaging 5 epochs is shown as well.   Although the signal averaging procedures improves the Signal-To-Noise-Radio (SNR) of the ErrP response, it reduces the number of data samples.  It produces a clear improvement only for the OHCs that contain more samples (1, 3 and 7).

\begin{figure}[ht]
    \centering
    \includegraphics[scale=0.12]{revisedimages/cross_val.eps}
    \caption{Binary single trial classification score using five different classifiers while recognizing ErrP potentials for the eight OHCs.  The classification score using an ensemble average of 5 epochs is shown as well (GrandAvg). Chance Level is 0.5.}
    \label{fig:classifiers}
\end{figure}

On the other hand, Figure \ref{fig:avg_steps} shows for each OHC the average amount of steps the agent takes to reach the goal as the Q-Table is progressively trained using the reward information obtained from the prediction performed by the trained classifier. Each point corresponds to a run session where the average number of steps, in 200 repetitions, that it takes for the agent to reach the goal for a specific Q-Table, is specified. The first point at 0 represents the amount of steps the agent takes to reach the goal for a Q-Table that hasn't been trained at all, where movements are decided randomly. The next point corresponds to the amount of steps it takes to reach the goal using a policy derived from a Q-Table trained after one brainwave session match, and so on.

\begin{figure}[h!]
\begin{subfigure}{0.5\textwidth}
\centering
\includegraphics[scale=0.27]{Images/Average_steps/a.png}
\includegraphics[scale=0.27]{Images/Average_steps/b.png}
\centering
\includegraphics[scale=0.27]{Images/Average_steps/c.png}
 \includegraphics[scale=0.27]{Images/Average_steps/d.png} 
 \centering
  \includegraphics[scale=0.27]{Images/Average_steps/e.png} 
  \includegraphics[scale=0.27]{Images/Average_steps/f.png} 
  \centering
  \includegraphics[scale=0.27]{Images/Average_steps/g.png} 
  \includegraphics[scale=0.27]{Images/Average_steps/h.png} 
\end{subfigure}
\caption{Average number of steps for the agent to reach the goal when trained with rewards generated from brainwaves from OHCs 1-8. Y axis show the averaged number of steps for a run session, while x axis show the number of game matches used to cumulative train the Q-Table.}
\label{fig:avg_steps}
\end{figure}

@@

\begin{figure}[h!]
\centering
\includegraphics[scale=0.4]{Images/Average_steps/noise.eps}
\caption{Average number of steps for the agent to reach the goal when trained with a classifier produced from sham EEG signals. X axis show the number of gaming agent training matches used to train the Q-Table.}
\label{fig:avg_steps_noise}
\end{figure}
